A Comparison of Graph Processing Systems

### 2020-09-16 documentation/paper/sections/results/bfs.tex
sssp und bfs nochmal überarbeitet, das fasse ich hoffentlich nicht mehr an

\subsection{Breadth-first search}
As with our results for SSSP, for BFS we will begin with our single-node results before looking at the distributed scenario. Lastly we will compare the two cases.
\subsubsection{Single-Node}
\begin{figure*}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_calcTime.png}
		\caption{Calculation time}
		\label{fig:singleNodeBFS_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_execTime.png}
		\caption{Execution time}
		\label{fig:singleNodeBFS_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_overheadTime.png}
		\caption{Overhead time}
		\label{fig:singleNodeBFS_overheadNormalized}
	\end{subfigure}
	\caption{Average times for BFS on a single computation node, black bars represent one standard deviation in our testing}
\end{figure*}
Just like with SSSP, Giraph ran out of memory ($>$250 GB) on any graph larger than wikipedia. Also, Polymer failed to complete on rMat28. Ligra, that failed during SSSP however completed our benchmark for BFS.

The calculation times provided in \autoref{fig:singleNodeBFS_calc} show Gemini and Ligra to be comparable in their performance. 
Their computation times deviate less than 151ms on all graphs except wikipedia and rMat28, wight Ligra being the faster framework on most graphs.
Ligra is 39ms faster on orkut, 2ms on twitter, 50ms on rMat27 and 151ms on friendster.
In turn, Gemini is 17 ms faster than Ligra on flickr.
Only on wikipedia and rMat28, there is a noticeable difference between the two frameworks. Ligra is 1.2s (7.8$\times$) faster than Gemini on wikipedia and 696ms (4.4$\times$) faster on rMat28.

For the remaining frameworks, we compare to Ligra since it is generally slightly faster than Gemini.
Giraph and Polymer are one to two orders of magnitude slower than both Ligra or Gemini. The only exception to this is Polymer on flickr, here Polymer is just 24ms (35\%) slower than Ligra.
Giraph takes 13$\times$, 32$\times$ and 27$\times$ longer than Ligra on flickr, orkut and wikipedia respectively.
As we said, Polymer is comparable to Ligra on flickr, for the other graphs however, its computation times are even longer than those of Giraph. The upside is though, that Polymer managed -- contrary to Giraph -- to finish computation on some larger graphs.
Polymer takes 55$\times$ longer on orkut, 60$\times$ on wikipedia, 129$\times$ on twitter, 530$\times$ on rMat27 and 240$\times$ on friendster. 
Especially interesting is here the difference between the times of rMat27 and friendster. There are 20\% (439M) edges more in friendster, yet the computation for the synthetic rMat27 takes 42\% longer.

Galois calculation performance is comparable to Gemini or Ligra on the smaller three graphs (flickr, orkut and wikipedia).
On the larger graphs however, Galois is slower than Gemini or Ligra but always faster than Polymer by one order of magnitude.

\subsubsection{Distributed}
\begin{figure*}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_calcTime.png}
		\caption{Calculation time}
		\label{fig:distributedBFS_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_execTime.png}
		\caption{Execution time}
		\label{fig:distributedBFS_exec}
	\end{subfigure}
	\hfil
	% \begin{subfigure}{0.3\textwidth}
	% 	\includegraphics[width=\linewidth]{../../plots/distributedBFS_overheadTimeNormalized.png}
	% 	\caption{Overhead time normalized by the graph size in million edges}
	% 	\label{fig:distributedBFS_overheadNormalized}
	% \end{subfigure}
	\caption{Average times for BFS on the distributed cluster, black bars represent one standard deviation in our testing}
	\label{fig:distributedBFS}
\end{figure*}
For both the calculation and the execution times, Breadth-First Search shows similar behaviour as the distributed SSSP test case. This is expected since both are graph traversal algorithms starting in one source vertex.
Hence, calculation complexity for each vertex and communication overhead is similar.
All measurements can be seen in \autoref{fig:distributedBFS}.

First, the calculation times in \autoref{fig:distributedBFS_calc}. It shows Giraph having the shortest calculation times on the real-world graphs, while Giraph's calculatin times on both rMat27 and rMat28 are the worst of all frameworks.

Comparing the execution times in \autoref{fig:distributedBFS_exec} results in the same findings as with SSSP.
While Gemini can compete with Galois on the small flickr graph, moving to larger data sets shows the worse performance of Gemini compared to Galois.

Much like when running SSSP, Giraph is slowest on all but one graph. Only on friendster is Gemini marginally slower, which was also the case for SSSP.

Both Galois implementations are again similar to the behaviour on SSSP.
Galois Push is generally faster than the Pull alternative while both Push and Pull versions are faster than Gemini and Giraph across all graphs.
This makes Galois Push the clear winner for distributed BFS.

>>>>

\subsection{Breadth-first search}
As with our results for SSSP, for BFS we will begin with our single-node results before looking at the distributed scenario.
\subsubsection{Single-Node}
\begin{figure*}
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_calcTime.png}
		\caption{Calculation time}
		\label{fig:singleNodeBFS_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_execTime.png}
		\caption{Execution time}
		\label{fig:singleNodeBFS_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/singleNodeBFS_overheadTime.png}
		\caption{Overhead time}
		\label{fig:singleNodeBFS_overheadNormalized}
	\end{subfigure}
	\caption{Average times for BFS on a single computation node, black bars represent one standard deviation in our testing}
\end{figure*}
Just like with SSSP, Giraph ran out of memory ($>$250 GB) on any graph larger than wikipedia. Also, Polymer failed to complete on rMat28. Ligra, that failed during SSSP however completed our benchmark for BFS.

The calculation times provided in \autoref{fig:singleNodeBFS_calc} show Gemini and Ligra to be comparable in their performance. 
Their computation times deviate less than 151ms on all graphs except wikipedia and rMat28, wight Ligra being the faster framework on most graphs.
Ligra is between 2ms (twitter) and 151ms (friendster) faster than Gemini.
In turn, Gemini is 17ms faster than Ligra on flickr.
Only on wikipedia and rMat28, there is a noticeable difference between the two frameworks. Ligra is 1.2s (7.8$\times$) faster than Gemini on wikipedia and 696ms (4.4$\times$) faster on rMat28.

For the remaining frameworks, we compare to Ligra since it is generally slightly faster than Gemini.
Giraph and Polymer are one to two orders of magnitude slower than both Ligra or Gemini. The only exception to this is Polymer on flickr, here Polymer is just 24ms (35\%) slower than Ligra.
Giraph takes between 13$\times$ and 32$\times$ longer than Ligra on flickr, orkut or wikipedia.
As we said, Polymer is comparable to Ligra on flickr, but for the other graphs, its computation times are even longer than those of Giraph. The upside is though, that Polymer managed -- contrary to Giraph -- to finish computation on some larger graphs.
Polymer takes between 55$\times$ and 530$\times$ longer than Ligra on the graphs larger than flickr.
Especially interesting is here the difference between the times of rMat27 and friendster. There are 20\% (439M) more edges in friendster, yet the computation for the synthetic rMat27 takes 42\% longer.

Galois calculation performance is comparable to Gemini or Ligra on the smaller three graphs (flickr, orkut and wikipedia).
Only on the larger graphs is Galois slower than Gemini or Ligra, meanwhile Galois is always faster than Polymer by one order of magnitude.

\subsubsection{Distributed}
\begin{figure*}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_calcTime.png}
		\caption{Calculation time}
		\label{fig:distributedBFS_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedBFS_execTime.png}
		\caption{Execution time}
		\label{fig:distributedBFS_exec}
	\end{subfigure}
	\hfil
	% \begin{subfigure}{0.3\textwidth}
	% 	\includegraphics[width=\linewidth]{../../plots/distributedBFS_overheadTimeNormalized.png}
	% 	\caption{Overhead time normalized by the graph size in million edges}
	% 	\label{fig:distributedBFS_overheadNormalized}
	% \end{subfigure}
	% \hfil
	\caption{Average times for BFS on the distributed cluster, black bars represent one standard deviation in our testing}
	\label{fig:distributedBFS}
\end{figure*}
For both the calculation and the execution times, Breadth-First Search shows similar behaviour as the distributed SSSP test case. This is expected since both are graph traversal algorithms starting in one source vertex.
Hence, calculation complexity for each vertex and communication overhead is similar. All measurements can be seen in \autoref{fig:distributedBFS}.

The results for calculation time (cf. \autoref{fig:distributedBFS_calc}) show Giraph to have very short calculation times on the real-world graphs, while Giraph's calculation times on both rMat27 and rMat28 are the worst of all frameworks. Thus, Giraph is fastest on the three smallest graphs and second fastest on twitter and friendster. On those two graphs, Gemini is fastest with only a small margin between the two frameworks.
Just like with SSSP, the Galois implementations have the longest calculation time on the real-world graphs. And Galois is second slowest, on the synthetic graphs.

Comparing the execution times in \autoref{fig:distributedBFS_exec} results again in similar findings to SSSP.
While Gemini can compete with Galois on the small flickr graph, moving to larger data sets shows the worse performance of Gemini compared to Galois.
Similar to SSSP, Giraph is slowest on all but one graph. Only on friendster is Gemini marginally slower, this was also the case for SSSP.
Galois Push is generally faster than the Pull alternative while both Push and Pull versions are faster than Gemini and Giraph across all graphs.
This makes Galois Push the clear winner for distributed BFS.

### 2020-09-16 documentation/paper/sections/results/sssp.tex
kleine fixes, normalisierung in sssp von overhead zu exec
kleine änderungen
sssp und bfs nochmal überarbeitet, das fasse ich hoffentlich nicht mehr an

Comparing the other frameworks (i.e. excluding Giraph in the further comparisons), shows them to perform similar on the smaller graphs. There, the average calculation times of the four frameworks (Galois, Gemini, Ligra, Polymer) are 35ms on flickr, 77ms on orkut, 538ms on wikipedia. 
The four frameworks are always within $x$ ms of this average. Galois and Gemini being 24ms and 12ms faster than the average. Ligra and Polymer are slower by 27ms and 9ms.
Orkut is the graph where all the four frameworks are within 20ms of their average, Galois being the outlier at 19ms slower than average.
For wikipedia, Galois and Ligra are close to each other, while Gemini is 560ms (104\%) slower than the average of the four frameworks.
And Polymer is the fastest framework on wikipedia, being 330ms (61\%) faster than the others.
For the larger graphs, Polymer has the shortest computation time as well. Gemini is second, taking about 1.9$\times$ times the computation time of Polymer on twitter and friendster while being equally fast (8\% longer) on rMat27. Galois and Ligra however have much longer computation times compared to Polymer. Galois takes anywhere from 3.3$\times$ (twitter) to 4.2$\times$ (friendster) the computation time of Polymer.
Ligra requires 9.8$\times$, 7.0$\times$ and 3.2$\times$ the computation time of Polymer on twitter, rMat27 and friendster respectively. This makes Ligra the slowest Framework on twitter and rMat27. Galois is the slowest on friendster.
However, while especially Galois is comparably slow to Polymer in the computation time, it is important to keep in mind that Polymer could not finish computation on rMat28. Meanwhile both Gemini and Galois managed just fine.

Moving on to the execution times, which can be seen in \autoref{fig:singleNodeBFS_exec}. 
A general overview shows Galois as the clear winner on most graphs. It has the smalles computation times on all graphs except flickr, where Galois is 25ms (8\%) slower than Ligra. 
On the other 5 graphs however, Galois has the smaller execution time by one or sometimes even two orders of magnitude. 
For example, on orkut Galois requires 0.78s to execute, while Gemini takes 13.8s, Giraph takes 135.9s, Ligra takes 2.66s and Polymer takes 26.6s.
This goes on for the larger graphs, Ligra being second-fastest and Polymer and Gemini close together but both always at least one order of magnitude slower than Galois.

\subsubsection{Distributed}
\begin{figure*}
	\centering
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_calcTime.png}
		\caption{Calculation times}
		\label{fig:distributedSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_execTime.png}
		\caption{Execution times}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_overheadTime.png}
		\caption{Overhead times}
		\label{fig:distributedSSSP_overhead}
	\end{subfigure}
	\caption{Average times for SSSP on the distributed cluster, black bars represent one standard deviation in our testing.}
	\label{fig:distributedSSSP}
\end{figure*}

Moving on to the distributed cluster, \autoref{fig:distributedSSSP} shows the benchmark results as calculation and execution times.

Comparing the two Galois implementations, we find the calculation and execution times to be similar on smaller graphs and Push being the superior implementation for SSSP on larger data sets. Galois Pull being anywhere from just as fast to 3.5$\times$ slower on real-world data sets compared to the Push variant. The synthetic graphs are more extreme, execution times are close to 4$\times$ (rMat27) and 5$\times$ (rMat28) longer.

Both Galois implementations have significantly smaller execution times compared to Gemini or Giraph on all graphs (cf. \autoref{tbl:ssspexec}).
You can see Gemini being worse by at least a factor of 4 compared to Galois Push on all graphs except flickr.
Giraph's execution times in comparison to this are even worse, taking at least 7$\times$ longer than Galois Push on all graphs.

Evidently, Galois Push is the fastest algorithm in our lineup on 6 out of 7 graphs. With the exception being flickr, where Galois Push takes negligibly longer than the Pull counterpart.

\begin{table}
\renewcommand{\arraystretch}{1.2}
\tiny
\centering
\caption{Distributed SSSP Execution Times and their Realation to Galois Push}
\begin{tabular}{crrrrrrrr}
\hline
\bf{Data Set}&
\multicolumn{2}{c}{\bf Galois Push}&\multicolumn{2}{c}{\bf Galois Pull}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
&$\times$&(s)&$\times$&(s)&$\times$&(s)&$\times$&(s)\\\hline
flickr & 1.0 & (2.4) & 0.97 & (2.4) & 1.02 & (2.5) & 17.46 & (42.6)\\
orkut & 1.0 & (4.2) & 1.28 & (5.4) & 4.12 & (17.3) & 14.38 & (60.4)\\
wikipedia & 1.0 & (14.2) & 1.88 & (26.6) & 5.26 & (74.5) & 7.11 & (100.8) \\
twitter & 1.0 & (40.0) & 3.56 & (142.2) & 9.79 & (391.1) & 8.76 & (349.9)\\
rMat27 & 1.0 & (39.0) & 3.98 & (154.9) & 9.91 & (386.0) & 14.52 & (565.8)\\
friendster & 1.0 & (58.5) & 2.32 & (136.0) & 9.72 & (568.9) & 7.59 & (444.0)\\
rMat28 & 1.0 & (71.5) & 5.7 & (407.9) & 11.07 & (792.0) & 16.5 & (1180.2)\\\hline
\end{tabular}
\label{tbl:ssspexec}
\end{table}

When taking a closer look at Giraph, it seems to not cope well with synthetic data sets. Analyzing the computation times in \autoref{fig:distributedSSSP_calc}, we see that it is the fastest framework on our real-world graphs. And that with a considerable margin of other frameworks always taking at least 50\% longer (lower bound here is Gemini on flickr) up to Galois Pull needing 18$\times$ more time on wikipedia.
On both synthetic graphs however, Giraph is actually the slowest to compute. Giraph requires 12$\times$ or even 15$\times$ the computation time of Gemini on rMat27 or rMat28 respectively.

While Giraph's computation times are very competitive, when comparing the execution times in \autoref{fig:distributedSSSP_exec} we see that Giraph is actually the slowest framework on 5 out of 7 graphs. For the other two, namely twitter and friendster, Giraph is second slowest with only Gemini taking longer to complete.

Giraph and Gemini's very long execution times are only due to their overhead being many orders of magnitude larger than Galois overhead (\autoref{fig:distributedSSSP_overhead}).
Overhead for Gemini is greater than that of Galois on every graph. From just a 20\% increase on flickr up to friendster, where the overhead is 90$\times$ that of Galois Push.
For Giraph the overhead times are not as extreme but still generally worse. Even on flickr, Giraph's overhead time is already 23$\times$ that of Galois. On friendster, where Gemini was worst, Giraph \emph{only} requires 73$\times$ the overhead time of Galois.

\subsubsection{Single-Node vs. Distributed}
\todo{Vergleich}
\begin{itemize}
	\item GaloisPush vs Galois CPU // Galois Pull verliert bei Dist.
	\item Giraph vs. Giraph
	\item Gemini vs Gemini
\end{itemize}

>>>>

Comparing the other frameworks (i.e. excluding Giraph in the further comparisons), shows them to perform similar on the smaller graphs. There, the average calculation times of the four frameworks (Galois, Gemini, Ligra, Polymer) are 35ms on flickr, 77ms on orkut, 538ms on wikipedia. 
The four frameworks are close to this average for the smaller graphs. Galois and Gemini being 24ms and 12ms faster than the average. Ligra and Polymer are slower by 27ms and 9ms.
Orkut is the graph where all the four frameworks are within 20ms of their average, Galois being the outlier at 19ms slower than average.
For wikipedia, Galois and Ligra are close to each other, while Gemini is 560ms (104\%) slower than the average of the four frameworks.
And Polymer is the fastest framework on wikipedia, being 330ms (61\%) faster than the others.
For the larger graphs, Polymer has the shortest computation time as well. Gemini is second, taking about 1.9$\times$ times the computation time of Polymer on twitter and friendster while being equally fast (8\% longer) on rMat27. Galois and Ligra however have much longer computation times compared to Polymer. Galois takes anywhere from 3.3$\times$ (twitter) to 4.2$\times$ (friendster) the computation time of Polymer.
Ligra requires between 3.2$\times$ (friendster) and 9.8$\times$ (twitter) the computation time of Polymer on the larger graphs. This makes Ligra the slowest Framework on both twitter and rMat27. Galois is the slowest on friendster.
However, while especially Galois is comparably slow to Polymer in the computation time, it is important to keep in mind that Polymer could not finish computation on rMat28. Meanwhile both Gemini and Galois managed just fine.

The execution times show Galois to be the clear winner on most graphs (cf. \autoref{fig:singleNodeBFS_exec}).
It has the smallest computation times on all graphs except flickr, where Galois is 25ms (8\%) slower than Ligra. 
On the other 5 graphs however, Galois has the smaller execution time by one or sometimes even two orders of magnitude. 
For example, on orkut Galois requires 0.78s to execute, while the other frameworks require between 2.66s (Ligra) and 26.6s (Polymer).
This goes on for the larger graphs, Ligra being second-fastest. Polymer and Gemini close together but both always at least one order of magnitude slower than Galois.

\subsubsection{Distributed}
\begin{figure*}
	\centering
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_calcTime.png}
		\caption{Calculation times}
		\label{fig:distributedSSSP_calc}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_execTime.png}
		\caption{Execution times}
		\label{fig:distributedSSSP_exec}
	\end{subfigure}
	\hfil
	\begin{subfigure}{0.32\textwidth}
		\includegraphics[width=\linewidth]{../../plots/distributedSSSP_overheadTime.png}
		\caption{Overhead times}
		\label{fig:distributedSSSP_overhead}
	\end{subfigure}
	\caption{Average times for SSSP on the distributed cluster, black bars represent one standard deviation in our testing.}
	\label{fig:distributedSSSP}
\end{figure*}
On the distributed cluster, we find similar results as on the single node (cf. \autoref{fig:distributedSSSP}).
Both Galois implementations have significantly smaller execution times compared to Gemini or Giraph on all graphs (cf. \autoref{tbl:ssspexec}).
You can see Gemini being worse by at least a factor of 4 compared to Galois Push on all graphs except flickr.
Giraph's execution times in comparison to this are even worse, taking at least 7$\times$ longer than Galois Push on all graphs.
Comparing the two Galois implementations, we find the calculation and execution times to be similar on smaller graphs and Push being the superior implementation for SSSP on larger data sets. Galois Pull is anywhere from just as fast to 3.5$\times$ slower on real-world data sets compared to the Push variant. The synthetic graphs are more extreme. Execution times are close to 4$\times$ (rMat27) and 5$\times$ (rMat28) longer on Pull.
Evidently, Galois Push is the fastest algorithm in our lineup on 6 out of 7 graphs. With the exception being flickr, where Galois Push takes negligibly longer than the Pull counterpart.

\begin{table}
\renewcommand{\arraystretch}{1.2}
\tiny
\centering
\caption{Distributed SSSP Execution Times and Their Realation to Galois Push}
\begin{tabular}{crrrrrrrr}
\hline
\bf{Data Set}&
\multicolumn{2}{c}{\bf Galois Push}&\multicolumn{2}{c}{\bf Galois Pull}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
&$\times$&(s)&$\times$&(s)&$\times$&(s)&$\times$&(s)\\\hline
flickr & 1.0 & (2.4) & 0.97 & (2.4) & 1.02 & (2.5) & 17.46 & (42.6)\\
orkut & 1.0 & (4.2) & 1.28 & (5.4) & 4.12 & (17.3) & 14.38 & (60.4)\\
wikipedia & 1.0 & (14.2) & 1.88 & (26.6) & 5.26 & (74.5) & 7.11 & (100.8) \\
twitter & 1.0 & (40.0) & 3.56 & (142.2) & 9.79 & (391.1) & 8.76 & (349.9)\\
rMat27 & 1.0 & (39.0) & 3.98 & (154.9) & 9.91 & (386.0) & 14.52 & (565.8)\\
friendster & 1.0 & (58.5) & 2.32 & (136.0) & 9.72 & (568.9) & 7.59 & (444.0)\\
rMat28 & 1.0 & (71.5) & 5.7 & (407.9) & 11.07 & (792.0) & 16.5 & (1180.2)\\\hline
\end{tabular}
\label{tbl:ssspexec}
\end{table}

When taking a closer look at Giraph, it seems to not cope well with synthetic data sets. Analyzing the computation times in \autoref{fig:distributedSSSP_calc}, we see that it is the fastest framework on our real-world graphs. And that with a considerable margin of other frameworks always taking at least 50\% longer (lower bound here is Gemini on flickr) up to Galois Pull needing 18$\times$ more time on wikipedia.
On both synthetic graphs however, Giraph is actually the slowest to compute. Giraph requires 12$\times$ or even 15$\times$ the computation time of Gemini on rMat27 or rMat28 respectively.
While Giraph's computation times are very competitive, when comparing the execution times in \autoref{fig:distributedSSSP_exec} we see that Giraph is actually the slowest framework on 5 out of 7 graphs. For the other two, namely twitter and friendster, Giraph is second slowest with only Gemini taking longer to complete.
Giraph and Gemini's very long execution times are only due to their overhead being many orders of magnitude larger than Galois overhead (\autoref{fig:distributedSSSP_overhead}).
Overhead for Gemini is greater than that of Galois on every graph. From just a 20\% increase on flickr up to friendster, where the overhead is 90$\times$ that of Galois Push.
For Giraph the overhead times are not as extreme but still generally worse. Even on flickr, Giraph's overhead time is already 23$\times$ that of Galois. On friendster, where Gemini was worst, Giraph \emph{only} requires 73$\times$ the overhead time of Galois.
